Forecasting Influenza Hospitalizations Using a Bayesian Hierarchical Nonlinear Model with Discrepancy

### 2025-08-28 nonlinear_forecast.tex
add some score plots
finish responses to reviewers
update supplementary material
fix up arxiv manuscript

%%%%%%%%%%%packages added by Spencer%%%%%%%%%%%%%
\usepackage{booktabs} %for the table in the analysis section
\usepackage{enumerate} %for the short algorithm
\usepackage{subfigure} %for making plots with multiple images
\usepackage{tabularx} %for the spacing in tabular
\usepackage{newtxmath} %for making indicator function
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\pubyear{2024}
\arxiv{2010.00000}
\volume{TBA}
\issue{TBA}
\firstpage{1}
\lastpage{1}

@@

\begin{aug}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Only one address is permitted per author. %%
%% Only division, organization and e-mail is %%
%% included in the address.                  %%
%% Additional information can be included in %%
%% the Acknowledgments section if necessary. %%
%% ORCID can be inserted by command:         %%
%% \orcid{0000-0000-0000-0000}               %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\author[A]{\snm{Spencer Wadsworth}\ead[label=e1]{sgw96@iastate.edu}}
% \author[A]{\fnms{Second}~\snm{Author}\ead[label=e2]{second@somewhere.com}\orcid{0000-0000-0000-0000}}
\and
\author[A]{~\snm{Jarad Niemi}\ead[label=e2]{niemi@iastate.edu}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Addresses                                %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\address[A]{Department of Statistics,
Iowa State University, Ames, IA 50011}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Supplementary Material, including data   %%
%% sets and code, should be provided in     %%
%% {supplement} environment with title      %%
%% and short description. It cannot be      %%
%% available exclusively as external link.  %%
%% All Supplementary Material must be       %%
%% available to the reader on Project       %%
%% Euclid with the published article.       %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{supplement}
Supplement to "Forecasting Influenza Hospitalizations Using a
Bayesian Hierarchical Nonlinear Model with
Discrepancy"\\
A. Additional plots for ILI \& Hospitalization data for select regions, results 
from simulation study, and 2023-24 flu analysis\\
% \end{supplement}
B. Posterior distribution plots for select parameters\\
% \sdescription{2. Plots of posterior distributions for parameters in both ILI and hospitalization models}
C. FluSight forecast competition scoring results
\end{supplement}
% \begin{supplement}
% \stitle{3. FluSight forecast competition scoring results}
% \sdescription{Flu forecast results with relative weighted interval scoring rule similar to that used in  FluSight}
% \end{supplement}

>>>>

%%%%%%%%%%%packages added by Spencer%%%%%%%%%%%%%
\usepackage{booktabs} %for the table in the analysis section
\usepackage{enumerate} %for the short algorithm
\usepackage{subfigure} %for making plots with multiple images
\usepackage{tabularx} %for the spacing in tabular
\usepackage{newtxmath} %for making indicator function
\usepackage{changepage} %for adjusting the margins
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\pubyear{2025}
\arxiv{2412.14339}
\volume{TBA}
\issue{TBA}
\firstpage{1}
\lastpage{1}

@@

\begin{aug}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Only one address is permitted per author. %%
%% Only division, organization and e-mail is %%
%% included in the address.                  %%
%% Additional information can be included in %%
%% the Acknowledgments section if necessary. %%
%% ORCID can be inserted by command:         %%
%% \orcid{0000-0000-0000-0000}               %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\author[A]{\snm{Spencer Wadsworth}\ead[label=e1]{iac25002@uconn.edu}}
% \author[A]{\fnms{Second}~\snm{Author}\ead[label=e2]{second@somewhere.com}\orcid{0000-0000-0000-0000}}
\and
\author[B]{~\snm{Jarad Niemi}\ead[label=e2]{niemi@iastate.edu}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Addresses                                %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\address[A]{Department of Statistics,
University of Connecticut, Storrs, CT 06269}
\address[B]{Department of Statistics,
Iowa State University, Ames, IA 50011}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Supplementary Material, including data   %%
%% sets and code, should be provided in     %%
%% {supplement} environment with title      %%
%% and short description. It cannot be      %%
%% available exclusively as external link.  %%
%% All Supplementary Material must be       %%
%% available to the reader on Project       %%
%% Euclid with the published article.       %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{supplement}
Supplement to "Forecasting Influenza Hospitalizations Using a
Bayesian Hierarchical Nonlinear Model with
Discrepancy"\\
A. Additional plots for ILI \& Hospitalization data for select regions, results 
from simulation study, and 2023-24 flu analysis\\
% \end{supplement}
B. Prior distribution assignments\\
C. Posterior distribution plots for select parameters\\
% \sdescription{2. Plots of posterior distributions for parameters in both ILI and hospitalization models}
D. Comparison of ILI/hospitalization forecast model combinations\\
E. FluSight forecast competition scoring results in terms of WIS
\end{supplement}
% \begin{supplement}
% \stitle{3. FluSight forecast competition scoring results}
% \sdescription{Flu forecast results with relative weighted interval scoring rule similar to that used in  FluSight}
% \end{supplement}

### 2025-08-28 supplemental_res.tex
fix up arxiv manuscript

\begin{figure}[hbt!]
    \centering
    \includegraphics[scale=.5]{Images/hosp_vs_week.png}
    \caption{Weekly hospitalization counts for the 50 US states for the 2022 
    (grey) and 2023 (black) flu seasons}
    \label{fig:hosp_vs_week}
\end{figure}

@@

Figures \ref{fig:wis_cover_sum} and \ref{fig:state_and_date_wis} are 
similar to figures \ref{fig:lwis_cover_sum} and \ref{fig:state_and_date_lwis}
except that they show WIS scores instead of LWIS scores. The results of 
foreacst comparison for WIS scores is very similar to those of the LWIS in 
terms of how well the $ASGD_NORM2$ forecasts did relative to the others from
the FluSight competition.

    % \centering
    \begin{adjustwidth}{-1.2cm}{-1.5cm}
    \includegraphics[scale = .54]{Images/wis_cover_sum.png}
    \caption{a) Averaged over location and horizon weighted interval score
    (WIS) for each week during the season for the 21 models being compared. 
    Each grey line represents one model, but the ASGD\_NORM2 (blue),
    SIRD\_NORM2 (green), and 
    FluSight-baseline (red) are colored to stand out.
    b) Boxplots of all WIS scores for 1, 2, 3, and 4-week ahead horizons 
    for the ASGD\_NORM2 (blue) and FluSight-baseline (red) models. 
    To improve vizualization, the $y$-axis
    is on the log scale.}
    \end{adjustwidth}
    \label{fig:wis_cover_sum}
\end{figure}

@@

>>>>

\begin{figure}[hbt!]
    \centering
    \includegraphics[scale=.5]{Images/hosp_vs_week.png}
    \caption{Weekly hospitalization counts for the 50 US states for the 2022 
    (grey) and 2023 (black) flu seasons.}
    \label{fig:hosp_vs_week}
\end{figure}

@@

Figures \ref{fig:wis_cover_sum1} and \ref{fig:state_and_date_wis} are 
similar to figures the main figures in the 2023 flu forecast assessment in the 
main text
except that they show WIS scores instead of LWIS scores. The results of 
foreacst comparison for WIS scores is very similar to those of the LWIS in 
terms of how well the ASGD\_NORM2 forecasts did relative to the others from
the FluSight competition.

\begin{figure}[hbt!]
\begin{adjustwidth}{-1.2cm}{-1.5cm}
    % \begin{minipage}{\linewidth}
    \centering
    \makebox[\linewidth][l]{
    \includegraphics[scale = .54]{Images/wis_cover_sum.png}
    }
    \end{adjustwidth}
    \caption{a) Averaged over location and horizon weighted interval score
    (WIS) for each week during the season for the 21 models being compared.
    Each grey line represents one model, but the ASGD\_NORM2 (blue),
    SIRD\_NORM2 (green), and
    FluSight-baseline (red) are colored to stand out.
    b) Boxplots of all WIS scores for 1, 2, 3, and 4-week ahead horizons
    for the ASGD\_NORM2 (blue), SIRD\_NORM2 (green), and
    FluSight-baseline (red) models.
    To improve vizualization, the $y$-axis
    is on the log scale.}
    \label{fig:wis_cover_sum1}
    % \end{minipage}

@@

% \begin{figure}[hbt!]
%     \label{fig:wis_cover_sum1}
%     % \centering
%     \begin{adjustwidth}{-1.2cm}{-1.5cm}
%     \includegraphics[scale = .54]{Images/wis_cover_sum.png}
%     \caption{a) Averaged over location and horizon weighted interval score
%     (WIS) for each week during the season for the 21 models being compared. 
%     Each grey line represents one model, but the ASGD\_NORM2 (blue),
%     SIRD\_NORM2 (green), and 
%     FluSight-baseline (red) are colored to stand out.
%     b) Boxplots of all WIS scores for 1, 2, 3, and 4-week ahead horizons 
%     for the ASGD\_NORM2 (blue), SIRD\_NORM2 (green), and
%     FluSight-baseline (red) models. 
%     To improve vizualization, the $y$-axis
%     is on the log scale.}
%     \end{adjustwidth}
%     
% \end{figure}
